Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-21 bb494/manuscript.tex
more to intro

\section{New Introduction}
Catalase is a

Understanding the optimizations of ubiquitous enzymes tells us how nature optimizes enzymes, and perhaps how faster-than-diffusion enzymes work
In particular, understanding how the long-range electric fields between two molecules might be used for biological purpose is interesting. Typically amino acids are quantified by their polarity, pka, bulk. E-field is a new mechanism of interest.
Catalase's tight perpendicular channel has a variety of optimizations:
   it evolved to concentrate H2O2 near its channel
   it is small, only allowing a couple solvent molecules through at once
   it uses two channels, one for reactant entrance and the other for product exit
   it uses hydrophobicity to prevent water from getting in, optimizing the H2O2 concentration in its heme pocket
   It uses an electric field to orient the chain of solvent molecules for optimal transmission and chemistry, even away from the heme

@@

\section{Results}
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:pure-gel}. The expected band corresponding to an 84-kD protein is seen across all lanes, indicating the presence of a catalase single subunit in each cell line. Contaminant bands in the gel are very faint, indicating pure protein.\\

@@

>>>>

\section{New Introduction}
Understanding the optimizations of ubiquitous enzymes tells us how nature optimizes enzymes, and perhaps how faster-than-diffusion enzymes work
In particular, understanding how the long-range electric fields between two molecules might be used for biological purpose is interesting. Typically amino acids are quantified by their polarity, pka, bulk. E-field is a new mechanism of interest.
Catalase's tight perpendicular channel has a variety of optimizations:
   it evolved to concentrate H2O2 near its channel
   it is small, only allowing a couple solvent molecules through at once
   it uses two channels, one for reactant entrance and the other for product exit
   it uses hydrophobicity to prevent water from getting in, optimizing the H2O2 concentration in its heme pocket
   It uses an electric field to orient the chain of solvent molecules for optimal transmission and chemistry, even away from the heme

First para
- reaction, relevance, structure, heme, conservation in nature

2nd para
- (talking about HPII) mechanism, channel, active site

3rd para
- catalase is FAST
- evolutionary optimizations
- why they are interesting
- what we intend to study, and why it is intersesting

4th para
- our intended experiment, wrt the dielectric constant work

5th para
- our ncAA experiment, and how if we can destroy the dielectric variance of catalase via AA addition
- how ncAAs are incorporated

Catalase is an enzyme which catalyzes the breakdown of hydrogen peroxide into water and oxygen gas. This is an important detoxification reaction, since hydrogen peroxide is a reactive toxin generated by several biological processes. Catalase is a tetrameric protein which uses a heme group in its active site to facilitate the breakdown of hydrogen peroxide.

@@

\section{Results}
to add: Chemical nature and location of your ncAAs in the structure. (This might fit best in results).
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:pure-gel}. The expected band corresponding to an 84-kD protein is seen across all lanes, indicating the presence of a catalase single subunit in each cell line. Contaminant bands in the gel are very faint, indicating pure protein.\\

@@

Want: 6-8 substrate concentrations; 3 repeats

Hypothesis: can we control catalase catalytic efficiency by modulating dielectric constant, thus dampening the effects of electric field between Asp and the heme?
salt vs dielectric const: Dielectric Relaxation of Aqueous NaCl Solutions, Buchner, May, 10.1021/jp982977k
temp vs dielectric const: Dielectric Constant of Water from 0 0 to 1000 C , Malmberg, Mariott, eps = 87. 740 - 0.400081t + 9.398(10^-4)t^2 + 1.410(10^-6)t^3

Diffusion-Controlled Reactions of Enzymes, Wei-Zhu Zhong
klim: 1.8*10^-9

EFFECT OF pH UPON THE REACTION KINETICS OF THE ENZYME-SUBSTRATE COMPOUNDS OF CATALASE*
Catalase reaction rate is constant at pH 5-9

New hypothesis: Catalase supposedly benefits from an electric field pointing through its active channel to properly position its substrate. We hypothesize that by destroying this electric field by inserting negatively charged groups near the heme, we can lower the reaction rate, possibly below the diffusion limit.
Catalase has constant activity between pH 5 through 9. We will insert a group with pKa of 7, which should be neutral at pH 6 and mostly positive at pH 8. If such an enzyme experiences a drop in catalytic efficiency between pH 7 and 9, this will be evidence of the importance of an electric field orienting substrate molecules.

3NY pka: 7.230 on the hydroxy group, Conversion of 3-nitrotyrosine to 3-aminotyrosine in peptides and proteins, Vallee

Site-Specific Incorporation of 3-Nitrotyrosine as a Probe of pKa Perturbation of Redox-Active Tyrosines in Ribonucleotide Reductase, Stubbe
pKa of 3NY can vary lots, between 7.5-10
